\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-06-02 paper/ms.tex
Mention template argument
New figure, posterior for N

\begin{CodeChunk}
\begin{CodeInput}
class MyModel
{
	private:
        DNest4::RJObject<MyConditionalPrior> gaussians;
....
\end{CodeInput}
\end{CodeChunk}

The specific prior for $N$ was
\begin{align}
p(N) \propto \frac{1}{N+1}
\end{align}
for $N \in \{1, 2, ..., 100\}$.

@@

The priors for the parameters given the hyperparameters were:
\begin{align}
\mu_j &\sim \textnormal{Laplace}(a_\mu, b_\mu)\\
\ln\sigma_j &\sim \textnormal{Laplace}(a_{\ln\sigma}, b_{\ln\sigma})\\
\ln W_j &\sim \textnormal{Laplace}(0, b_{\ln W}).
\end{align}

A Laplace (or bi-exponential)
distribution with location parameter $a$ and scale parameter
$b$ has density
\begin{align}
p(x | a, b) &= \frac{1}{2}\exp\left(-\frac{1}{b}|x - a|\right).
\end{align}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.6\textwidth]{figures/galaxies.pdf}
\caption{\label{fig:galaxies}}
\end{center}
\end{figure}

>>>>

\begin{CodeChunk}
\begin{CodeInput}
class MyModel
{
	private:
        DNest4::RJObject<MyConditionalPrior> gaussians;
....
\end{CodeInput}
\end{CodeChunk}
where the template argument \code{<MyConditionalPrior>}
is a class implementing the prior for the hyperparameters
$\alpha$ and the form of the conditional prior $p(x_i | \alpha)$.

The specific prior for $N$ was
\begin{align}
p(N) \propto \frac{1}{N+1}
\end{align}
for $N \in \{1, 2, ..., 100\}$.
For the conditional prior of the gaussian parameters,
we used Laplace (biexponential)
distributions\footnote{A Laplace
distribution with location parameter $a$ and scale parameter
$b$ has density $p(x | a, b) = \frac{1}{2}\exp\left(-\frac{1}{b}|x - a|\right)$.}

\begin{align}
\mu_j &\sim \textnormal{Laplace}(a_\mu, b_\mu)\\
\ln\sigma_j &\sim \textnormal{Laplace}(a_{\ln\sigma}, b_{\ln\sigma})\\
\ln W_j &\sim \textnormal{Laplace}(0, b_{\ln W}).
\end{align}

@@

@@

\begin{figure}
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=0.95\textwidth]{figures/galaxies.pdf}
\caption{The `galaxy' data, with some illustrative fits drawn
from the posterior distribution.\label{fig:galaxies}}
\end{minipage} \hspace{0.05\textwidth}
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=0.95\textwidth]{figures/galaxies_N.pdf}
\caption{The posterior distribution for $N$ given the
galaxy data.\label{fig:galaxies_N}}
\end{minipage}
\end{figure}
